---
title: "ARB,CHI,BUR"
output:
  pdf_document: default
  html_document: default
date: "2023-04-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      tidy = FALSE,
                      size = "small")
```

## Loading Libraries and Data

First, we load our libraries:

```{r}
library(tidyverse)
library(ggrepel)
library(broom)
library(GGally)
library(purrr)
```

Now we need to import our data set, and create data sets containing just data on McDonalds, Sonic and DQ respecively:

```{r}
#Loading in the CSV
nutritional_data <-  read.csv("data/nutritioninfo.csv")

#Arby's Data Set For 2-way clusters
arb_nutrition <- nutritional_data %>%
  filter(restaurant == "Arbys")%>%
  select(item, protein, calories)

#Arby's Data Set for all variables
arb_nutrition_data <- nutritional_data %>%
  filter(restaurant == "Arbys")

#Burger King Data Set for 2-way clusters
bk_nutrition <- nutritional_data %>%
  filter(restaurant == "Burger King")%>%
  select(item, protein, calories)

#Burger King Data Set for all variables
bk_nutrition <- nutritional_data %>%
  filter(restaurant == "Burger King")

#Chick Fila Data set
chf_nutrition <- nutritional_data %>%
   filter(restaurant == "Chick Fil-A")%>%
  select(item, protein, calories)

#Chick Fila Data Set for all variables
chf_nutrition_data <- nutritional_data %>%
   filter(restaurant == "Chick Fil-A")
```

# McDonald's K-Means Clustering

Now, We are going to make elbow plots to decide how many clusters we want for each McDonalds:

```{r}
arb_clusters_data <- arb_nutrition %>% 
  select(calories, protein)%>%
  drop_na

# Iterate through clustering algorithm for 10 different values of k
elbow_plot1 <- tibble(k = 1:10) %>%
  mutate(
    # List-column of 10 kmeans objects 
    # (apply `kmeans()` to each value of `k`)
    kmeans_arb = purrr::map(k, ~kmeans(arb_clusters_data, .x, nstart = 20)),
    # List-column of "glanced" model summaries for each kmeans object
    # (apply `glance()` to each corresponding result after running `kmeans()`)
    glanced = purrr::map(kmeans_arb, glance)) %>% 
  # Turn `glanced` list-column into regular tibble columns
  unnest(cols = c(glanced))

# Construct elbow plot
ggplot(elbow_plot1, aes(x = k, y = tot.withinss)) +
  geom_point() + 
  geom_line() +
  scale_x_continuous(breaks = 1:10) +
  labs(x = "Number of clusters (k)", 
       y = "Total within-cluster sum of squares")

```

> Based on the Elbow Plot Above, I am going to use four clusters, because there is still a large jump from three clusters to four, but then a very small jump between four clusters and five clusters.

## Now we are going to cluster based on calories and protein, and create a graph and a list of which items are in which clusters
```{r}
# set the seed for reproducibility
set.seed(23)

# Perform k-means clustering with k = 4
arb_clusters_4 <- arb_clusters_data %>% 
  kmeans(centers = 4, nstart = 20)

arb_clusters_c4 <- augment(arb_clusters_4, arb_nutrition)

ggplot(arb_clusters_c4, aes(x = calories, y = protein)) + 
  geom_point(aes(color = .cluster)) +
  geom_text_repel(aes(label = item, color = .cluster), 
                  size = 2, max.overlaps = 200, show.legend = FALSE) +
  scale_x_continuous(breaks = scales::breaks_width(200)) +
  scale_y_continuous(breaks = scales::breaks_width(25)) +
  # Add centroid labels to plot
  geom_label(data = arb_clusters_c4, aes(label = "", color = ""),
             size = 0.1,
             label.r = unit(0.05, "lines"),
             label.size = 0.5,
             label.padding = unit(0.05, "lines"),
             show.legend = FALSE) +
  labs(title = "Arbys Menu Items Grouped Based on Calories and Protein",
       x = "Calories",
       y = "Protein",
       color = "Cluster") +
  theme_classic() +
  xlim(c(0,1500)) +
      ylim(c(0,100))

#Get Important Data Points and What items are in which cluster
arb_summaries <- tidy(arb_clusters_4)
arb_summaries

arb_clusters_4$centers

cluster_list <- split(arb_nutrition$item, arb_clusters_4$cluster)
cluster_list
```



# Now we repeat the same process with Burger King:

## First an elbow plot to find the best number of clusters to use
```{r}
bk_clusters_data <- bk_nutrition %>% 
  select(calories, protein)%>%
  drop_na

# Iterate through clustering algorithm for 10 different values of k
elbow_plot2 <- tibble(k = 1:10) %>%
  mutate(
    # List-column of 10 kmeans objects 
    # (apply `kmeans()` to each value of `k`)
    kmeans_bk = purrr::map(k, ~kmeans(bk_clusters_data, .x, nstart = 20)),
    # List-column of "glanced" model summaries for each kmeans object
    # (apply `glance()` to each corresponding result after running `kmeans()`)
    glanced = purrr::map(kmeans_bk, glance)) %>% 
  # Turn `glanced` list-column into regular tibble columns
  unnest(cols = c(glanced))

# Construct elbow plot
ggplot(elbow_plot2, aes(x = k, y = tot.withinss)) +
  geom_point() + 
  geom_line() +
  scale_x_continuous(breaks = 1:10) +
  labs(x = "Number of clusters (k)", 
       y = "Total within-cluster sum of squares")
```

> Based on this elbow plot I am going to use three clusters because again there is a large drop in within-cluster sum of squares, and not a very large drop from 3 to four.

## Now we are going to cluster based on calories and protein, and create a graph and a list of which items are in which clusters
```{r}
# set the seed for reproducibility
set.seed(23)

# Perform k-means clustering with k = 3
bk_clusters_3 <- bk_clusters_data %>% 
  kmeans(centers = 3, nstart = 20)

bk_clusters_c3 <- augment(bk_clusters_3, bk_nutrition)

ggplot(bk_clusters_c3, aes(x = calories, y = protein)) + 
  geom_point(aes(color = .cluster)) +
  geom_text_repel(aes(label = item, color = .cluster), 
                  size = 2, max.overlaps = 200, show.legend = FALSE) +
  scale_x_continuous(breaks = scales::breaks_width(200)) +
  scale_y_continuous(breaks = scales::breaks_width(25)) +
  # Add centroid labels to plot
  geom_label(data = bk_clusters_c3, aes(label = "", color = ""),
             size = 0.1,
             label.r = unit(0.05, "lines"),
             label.size = 0.5,
             label.padding = unit(0.05, "lines"),
             show.legend = FALSE) +
  labs(title = "Burger King Menu Items Grouped Based on Calories and Protein",
       x = "Calories",
       y = "Protein",
       color = "Cluster") +
  theme_classic() +
  xlim(c(0,2500)) +
      ylim(c(0,90))

#Get Important Data Points and What items are in which cluster
bk_summaries <- tidy(bk_clusters_3)
bk_summaries

bk_clusters_3$centers

cluster_list <- split(bk_nutrition$item, bk_clusters_3$cluster)
cluster_list
```


# Now we are going to do the same process but with Chick Fila:

## First an elbow plot to determin number of clusters:

```{r}
chf_clusters_data <- chf_nutrition %>% 
  select(calories, protein)%>%
  drop_na

# Iterate through clustering algorithm for 10 different values of k
elbow_plot3 <- tibble(k = 1:10) %>%
  mutate(
    # List-column of 10 kmeans objects 
    # (apply `kmeans()` to each value of `k`)
    kmeans_chf = purrr::map(k, ~kmeans(chf_clusters_data, .x, nstart = 20)),
    # List-column of "glanced" model summaries for each kmeans object
    # (apply `glance()` to each corresponding result after running `kmeans()`)
    glanced = purrr::map(kmeans_chf, glance)) %>% 
  # Turn `glanced` list-column into regular tibble columns
  unnest(cols = c(glanced))

# Construct elbow plot
ggplot(elbow_plot3, aes(x = k, y = tot.withinss)) +
  geom_point() + 
  geom_line() +
  scale_x_continuous(breaks = 1:10) +
  labs(x = "Number of clusters (k)", 
       y = "Total within-cluster sum of squares")

```


> For Chick-Fila I am going to use 3 clusters because while there is not a large jump between 2 and 3 clusters there is a relatively small jump from 3 to 4.


## Now we are going to cluster based on calories and protein, and create a graph and a list of which items are in which clusters

```{r}
# set the seed for reproducibility
set.seed(23)

# Perform k-means clustering with k = 3
chf_clusters_3 <- chf_clusters_data %>% 
  kmeans(centers = 3, nstart = 20)

chf_clusters_c3 <- augment(chf_clusters_3, chf_nutrition)

ggplot(chf_clusters_c3, aes(x = calories, y = protein)) + 
  geom_point(aes(color = .cluster)) +
  geom_text_repel(aes(label = item, color = .cluster), 
                  size = 2, max.overlaps = 200, show.legend = FALSE) +
  scale_x_continuous(breaks = scales::breaks_width(200)) +
  scale_y_continuous(breaks = scales::breaks_width(25)) +
  # Add centroid labels to plot
  geom_label(data = chf_clusters_c5, aes(label = "", color = ""),
             size = 0.1,
             label.r = unit(0.05, "lines"),
             label.size = 0.5,
             label.padding = unit(0.05, "lines"),
             show.legend = FALSE) +
  labs(title = "Chick Fila Menu Items Grouped Based on Calories and Protein",
       x = "Calories",
       y = "Protein",
       color = "Cluster") +
  theme_classic() +
  xlim(c(0,1000)) +
      ylim(c(0,60))

#Get Important Data Points and What items are in which cluster
chf_summaries <- tidy(chf_clusters_3)
chf_summaries

chf_clusters_3$centers

cluster_list <- split(chf_nutrition$item, chf_clusters_3$cluster)
cluster_list
```

