---
title: "DQ, McDonalds, Sonic Clusters"
output: pdf_document
date: "2023-04-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE)
```

## Loading Libraries and Data

First, we load our libraries:

```{r}
library(tidyverse)
library(ggrepel)
library(broom)
library(GGally)
library(purrr)
```

Now we need to import our data set, and create data sets containing just data on McDonalds, Sonic and DQ respecively:

```{r}
#Loading in the CSV
nutritional_data <-  read.csv("data/nutritioninfo.csv")

#McDonald's Data Set For 2-way clusters
mcd_nutrition <- nutritional_data %>%
  filter(restaurant == "Mcdonalds")%>%
  select(item, protein, calories)

#McDonald's Data Set for all variables
mcd_nutrition_data <- nutritional_data %>%
  filter(restaurant == "Mcdonalds")

#Dairy Queen Data Set for 2-way clusters
dq_nutrition <- nutritional_data %>%
  filter(restaurant == "Dairy Queen")%>%
  select(item, protein, calories)

#Dairy Queen Data Set for all variables
dq_nutrition <- nutritional_data %>%
  filter(restaurant == "Dairy Queen")

#Sonic Data set
sonic_nutrition <- nutritional_data %>%
   filter(restaurant == "Sonic")%>%
  select(item, protein, calories)

#Sonic Data Set for all variables
sonic_nutrition_data <- nutritional_data %>%
   filter(restaurant == "Sonic")
```

#McDonald's K-Means Clustering

Now, We are going to make elbow plots to decide how many clusters we want for each McDonalds:

```{r}
mcd_clusters_data <- mcd_nutrition %>% 
  select(calories, protein)%>%
  drop_na

# Iterate through clustering algorithm for 10 different values of k
elbow_plot1 <- tibble(k = 1:10) %>%
  mutate(
    # List-column of 10 kmeans objects 
    # (apply `kmeans()` to each value of `k`)
    kmeans_mcd = purrr::map(k, ~kmeans(mcd_clusters_data, .x, nstart = 20)),
    # List-column of "glanced" model summaries for each kmeans object
    # (apply `glance()` to each corresponding result after running `kmeans()`)
    glanced = purrr::map(kmeans_mcd, glance)) %>% 
  # Turn `glanced` list-column into regular tibble columns
  unnest(cols = c(glanced))

# Construct elbow plot
ggplot(elbow_plot1, aes(x = k, y = tot.withinss)) +
  geom_point() + 
  geom_line() +
  scale_x_continuous(breaks = 1:10) +
  labs(x = "Number of clusters (k)", 
       y = "Total within-cluster sum of squares")

```

> Based on the Elbow Plot Above, I am going to use four clusters, because there is still a large jump from three clusters to four, but then a very small jump between four clusters and five clusters.

##Now we are going to cluster based on calories and protein, and create a graph and a list of which items are in which clusters
```{r}
# set the seed for reproducibility
set.seed(23)

# Perform k-means clustering with k = 3
mcd_clusers_4 <- mcd_clusters_data %>% 
  kmeans(centers = 4, nstart = 20)

mcd_clusers_c4 <- augment(mcd_clusers_4, mcd_nutrition)

ggplot(mcd_clusers_c4, aes(x = calories, y = protein)) + 
  geom_point(aes(color = .cluster)) +
  geom_text_repel(aes(label = item, color = .cluster), 
                  size = 2, max.overlaps = 200, show.legend = FALSE) +
  scale_x_continuous(breaks = scales::breaks_width(200)) +
  scale_y_continuous(breaks = scales::breaks_width(25)) +
  # Add centroid labels to plot
  geom_label(data = mcd_clusers_c4, aes(label = "", color = ""),
             size = 0.1,
             label.r = unit(0.05, "lines"),
             label.size = 0.5,
             label.padding = unit(0.05, "lines"),
             show.legend = FALSE) +
  labs(title = "McDonalds Menu Items Grouped Based on Calories and Protein",
       x = "Calories",
       y = "Protein",
       color = "Cluster") +
  theme_classic() +
  xlim(c(0,4000)) +
      ylim(c(0,200))

#Get Important Data Points and What items are in which cluster
mcd_summaries <- tidy(mcd_clusers_4)
mcd_summaries

mcd_clusers_4$centers

cluster_list <- split(mcd_nutrition$item, mcd_clusers_4$cluster)
cluster_list
```



#Now we repeat the same process with sonic:

##First an elbow plot to find the best number of clusters to use
```{r}
sonic_clusters_data <- sonic_nutrition %>% 
  select(calories, protein)%>%
  drop_na

# Iterate through clustering algorithm for 10 different values of k
elbow_plot2 <- tibble(k = 1:10) %>%
  mutate(
    # List-column of 10 kmeans objects 
    # (apply `kmeans()` to each value of `k`)
    kmeans_sonic = purrr::map(k, ~kmeans(sonic_clusters_data, .x, nstart = 20)),
    # List-column of "glanced" model summaries for each kmeans object
    # (apply `glance()` to each corresponding result after running `kmeans()`)
    glanced = purrr::map(kmeans_sonic, glance)) %>% 
  # Turn `glanced` list-column into regular tibble columns
  unnest(cols = c(glanced))

# Construct elbow plot
ggplot(elbow_plot2, aes(x = k, y = tot.withinss)) +
  geom_point() + 
  geom_line() +
  scale_x_continuous(breaks = 1:10) +
  labs(x = "Number of clusters (k)", 
       y = "Total within-cluster sum of squares")
```

> Based on this elbow plot I am going to use three clusters because again there is a large drop in within-cluster sum of squares, and not a very large drop from 3 to four.

##Now we are going to cluster based on calories and protein, and create a graph and a list of which items are in which clusters
```{r}
# set the seed for reproducibility
set.seed(23)

# Perform k-means clustering with k = 3
sonic_clusers_3 <- sonic_clusters_data %>% 
  kmeans(centers = 3, nstart = 20)

sonic_clusers_c3 <- augment(sonic_clusers_3, sonic_nutrition)

ggplot(sonic_clusers_c3, aes(x = calories, y = protein)) + 
  geom_point(aes(color = .cluster)) +
  geom_text_repel(aes(label = item, color = .cluster), 
                  size = 2, max.overlaps = 200, show.legend = FALSE) +
  scale_x_continuous(breaks = scales::breaks_width(200)) +
  scale_y_continuous(breaks = scales::breaks_width(25)) +
  # Add centroid labels to plot
  geom_label(data = sonic_clusers_c3, aes(label = "", color = ""),
             size = 0.1,
             label.r = unit(0.05, "lines"),
             label.size = 0.5,
             label.padding = unit(0.05, "lines"),
             show.legend = FALSE) +
  labs(title = "Sonic Menu Items Grouped Based on Calories and Protein",
       x = "Calories",
       y = "Protein",
       color = "Cluster") +
  theme_classic() +
  xlim(c(0,2500)) +
      ylim(c(0,90))

#Get Important Data Points and What items are in which cluster
sonic_summaries <- tidy(sonic_clusers_3)
sonic_summaries

sonic_clusers_3$centers

cluster_list <- split(sonic_nutrition$item, sonic_clusers_3$cluster)
cluster_list
```


#Now we are going to do the same process but with Dairy Queen:

##First an elbow plot to determin number of clusters:

```{r}
dq_clusters_data <- dq_nutrition %>% 
  select(calories, protein)%>%
  drop_na

# Iterate through clustering algorithm for 10 different values of k
elbow_plot3 <- tibble(k = 1:10) %>%
  mutate(
    # List-column of 10 kmeans objects 
    # (apply `kmeans()` to each value of `k`)
    kmeans_dq = purrr::map(k, ~kmeans(dq_clusters_data, .x, nstart = 20)),
    # List-column of "glanced" model summaries for each kmeans object
    # (apply `glance()` to each corresponding result after running `kmeans()`)
    glanced = purrr::map(kmeans_dq, glance)) %>% 
  # Turn `glanced` list-column into regular tibble columns
  unnest(cols = c(glanced))

# Construct elbow plot
ggplot(elbow_plot3, aes(x = k, y = tot.withinss)) +
  geom_point() + 
  geom_line() +
  scale_x_continuous(breaks = 1:10) +
  labs(x = "Number of clusters (k)", 
       y = "Total within-cluster sum of squares")

```


> For Dairy Queen I am going to use five clusters because while there is not a large jump between 3 and 4 clusters there is a relatively large jump from 3 to 4.


##Now we are going to cluster based on calories and protein, and create a graph and a list of which items are in which clusters

```{r}
# set the seed for reproducibility
set.seed(23)

# Perform k-means clustering with k = 3
dq_clusers_5 <- dq_clusters_data %>% 
  kmeans(centers = 5, nstart = 20)

dq_clusers_c5 <- augment(dq_clusers_5, dq_nutrition)

ggplot(dq_clusers_c5, aes(x = calories, y = protein)) + 
  geom_point(aes(color = .cluster)) +
  geom_text_repel(aes(label = item, color = .cluster), 
                  size = 2, max.overlaps = 200, show.legend = FALSE) +
  scale_x_continuous(breaks = scales::breaks_width(200)) +
  scale_y_continuous(breaks = scales::breaks_width(25)) +
  # Add centroid labels to plot
  geom_label(data = dq_clusers_c5, aes(label = "", color = ""),
             size = 0.1,
             label.r = unit(0.05, "lines"),
             label.size = 0.5,
             label.padding = unit(0.05, "lines"),
             show.legend = FALSE) +
  labs(title = "Dairy Queen Menu Items Grouped Based on Calories and Protein",
       x = "Calories",
       y = "Protein",
       color = "Cluster") +
  theme_classic() +
  xlim(c(0,1500)) +
      ylim(c(0,60))

#Get Important Data Points and What items are in which cluster
dq_summaries <- tidy(dq_clusers_5)
dq_summaries

dq_clusers_5$centers

cluster_list <- split(dq_nutrition$item, dq_clusers_5$cluster)
cluster_list
```

